EDLD 651 Final Paper

### 2023-12-06 scripts/manuscript.qmd
Final Touches & Abstract
Added the citations needed, updated figure outputs to be the same theme, added figure #s, and abstract.

---
title: "manuscript"
format: pdf
editor: visual
author: "Leah Peterson, Alexus Rock, and Ben Pfingston"
bibliography: biblio.bib
warning : false
message : false
echo : false
---

@@

comm <- comm %>%
  mutate(ppis_total = ppis_1_score + ppis_2_score,
         age = as.numeric(age)) %>%  # Convert age column to numeric
  filter(!is.na(age))
```

@@

```{r}
ppis_ss_table <- communication %>%
select(ppis_1_score:ppis_total) %>%
  pivot_longer(
  cols = everything(),
  names_to = "measure",
  values_to = "score") %>%
  group_by(measure) %>%
  summarise(Mean = mean(score, na.rm = TRUE),
            SD = sd(score, na.rm = TRUE)) %>%
  pivot_longer(
    cols = -measure,
    names_to = "desc",
    values_to = "value"
    ) %>%
  pivot_wider(names_from = measure,
              values_from = value)
```

@@

```{r}
#| echo: false
#| warning: fale
#| message: false
mean_age <- mean(comm$age) %>% round(2)
sd_age <- sd(comm$age) %>% round(2)
```

@@

We used R (Version 4.3.2; @R) and the R-packages *ggplot2* [@ggplot], *here* [@here], *janitor* [@janitor], *rio* [@rio], and *tidyverse* [@tidy] for all our analyses.

@@

```{r}
#| label: scatterplot
#| warning: false
#| message: false
#| echo: false

@@

Gender differences existed for teacher invasive behaviors. Non-binary individuals perceived their teachers behaviors as being less invasive than females and males perceptions. Gender differences existed for teacher privacy invasion. Males perceived their teachers invading their privacy less than female and non-binary individuals. A boxplot of Teacher Invasive Behaviors scores, split by gender, can be found in Figure #. There were no gender differences in student defensive behaviors. A boxplot of this relationship can be found below in Figure #. There were also no differences in the total Teacher Privacy Invasion scale scores between gender groups, shown in the boxplot in Figure #.

There were gender differences in the amount of suspicion towards teachers. Females had the highest levels of suspicion towards their teachers, and non-binary individuals had the least amount of suspicion. A boxplot of mean Suspicion Scale scores, split by gender, can be found in Figure # below.

```{r boxplot-gender-ppis-1-score, warning=FALSE, echo=FALSE}

ggplot(communication, aes(gender, ppis_1_score, fill=gender)) +
  geom_boxplot() +
  theme(legend.position = "none") +
    scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
  labs(x = "Gender",
       y = "Teacher Invasive Behaviors Score",
       title = "Boxplot of Teacher Invasive Behaviors Score by Gender", 
       tag = "Figure 2.")
```

```{r boxplot-gender-ppis-2-score, warning=FALSE, echo=FALSE}

ggplot(communication, aes(gender, ppis_2_score, fill=gender)) +
  geom_boxplot() +
  theme(legend.position = "none") +
  scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
  labs(x = "Gender",
       y = "Student Defensive Behaviors Score",
       title = "Boxplot of Student Defensive Behaviors Score by Gender",
       tag = "Figure 3.")

@@

```{r boxplot-gender-ppis-total, warning=FALSE, echo=FALSE}

ggplot(communication, aes(gender, ppis_total, fill=gender)) +
  geom_boxplot() +
  theme(legend.position = "none") +
    scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
  labs(x = "Gender",
       y = "Teacher Privacy Invasion Scale Total",
       title = "Boxplot of Teacher Privacy Invasion Scale Total by Gender",
       tag = "Figure 4.")

@@

```{r boxplot-gender-ss-score, warning=FALSE, echo=FALSE}

ggplot(communication, aes(gender, ss_score, fill=gender)) +
  geom_boxplot() + 
  scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
  theme(legend.position="none") +
  labs(x = "Gender",
       y = "Suspicion Scale Score",
       title = "Boxplot of Suspicion Scale Score by Gender",
       tag = "Figure 5.")

@@

There were no gender differences in student defensive behaviors. Students were not more defensive towards their teachers depending on student gender.

>>>>

---
title: "EDLD 651 Final Paper"
format: pdf
editor: visual
author: "Leah Peterson, Alexus Rock, and Ben Pfingston"
bibliography: biblio.bib
warning : false
message : false
echo : false
---

@@

comm <- comm %>%
  mutate(ppis_total = ppis_1_score + ppis_2_score,
         age = as.numeric(age)) %>%  # Converting age column to numeric
  filter(!is.na(age))
```

@@

```{r}
ppis_ss_table <- communication %>%
select(ppis_1_score:ppis_total) %>%
  pivot_longer(
  cols = everything(),
  names_to = "measure",
  values_to = "score") %>%
  group_by(measure) %>%
  summarise(Mean = round(mean(score, na.rm = TRUE), 2),
            SD = round(sd(score, na.rm = TRUE),2)) %>%
  pivot_longer(
    cols = -measure,
    names_to = "desc",
    values_to = "value"
    ) %>%
  pivot_wider(names_from = measure,
              values_from = value)
```

# Abstract

By drawing on theories of gender socialization and trust violations, the current study explores the dynamics of trust and privacy invasions in student-teacher relationships. Additionally, this study aims to investigate how gender may impact a young adult's perception of these topics. We predict that individuals who are more trustworthy will perceive fewer privacy invasions from teachers in their life. A sample of 98 young adults from a Minnesota undergraduate student body participated in this study. To measure young adult perceptions of trustworthiness, prior teacher privacy invasions, and suspicion towards teachers, modified scales, including the Parental Privacy Invasions Scale and the Suspicion Scale, were used. The results indicate that self-reported trustworthiness does not significantly impact the perception of teacher privacy invasions. However, gender differences were observed in how individuals perceive and experience their teacher behaviors. This study adds to our understanding of the complex interplay between trust, gender, and privacy invasions in student-teacher relationships. Further, the findings emphasize the complexity of trust dynamics in student-teacher relationships and suggest young adults perceive and respond to invasive behaviors in educational settings differently based on their gender identity.

@@

```{r}
mean_age <- mean(comm$age) %>% round(2)
sd_age <- sd(comm$age) %>% round(2)
```

@@

We used R (Version 4.3.2; @R) and the R-packages *ggplot2* [@ggplot], *gt* [@gt], *gtExtras* [@gtE], *here* [@here], *janitor* [@janitor], *papaja* [@papaja], *rio* [@rio], and *tidyverse* [@tidy] for all our analyses.

@@

```{r}
#| label: scatterplot

@@

Gender differences existed for teacher invasive behaviors. Non-binary individuals perceived their teachers behaviors as being less invasive than females and males perceptions. Gender differences existed for teacher privacy invasion. Males perceived their teachers invading their privacy less than female and non-binary individuals. A boxplot of Teacher Invasive Behaviors scores, split by gender, can be found in Figure 2. There were no gender differences in student defensive behaviors. A boxplot of this relationship can be found below in Figure 3. There were also no differences in the total Teacher Privacy Invasion scale scores between gender groups, shown in the boxplot in Figure 4.

There were gender differences in the amount of suspicion towards teachers. Females had the highest levels of suspicion towards their teachers, and non-binary individuals had the least amount of suspicion. A boxplot of mean Suspicion Scale scores, split by gender, can be found in Figure 5 below.

```{r}
#| label: boxplot-gender-ppis-1-score

ggplot(communication, aes(gender, ppis_1_score, fill=gender)) +
  geom_boxplot() +
  theme(legend.position = "none") +
    scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
  labs(x = "Gender",
       y = "Teacher Invasive Behaviors Score",
       title = "Boxplot of Teacher Invasive Behaviors Score by Gender", 
       tag = "Figure 2.")+
  theme_minimal()
```

```{r}
#| label: boxplot-gender-ppis-2-score
ggplot(communication, aes(gender, ppis_2_score, fill=gender)) +
  geom_boxplot() +
  theme(legend.position = "none") +
  scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
  labs(x = "Gender",
       y = "Student Defensive Behaviors Score",
       title = "Boxplot of Student Defensive Behaviors Score by Gender",
       tag = "Figure 3.") +
  theme_minimal()

@@

```{r}
#| label: boxplot-gender-ppis-total

ggplot(communication, aes(gender, ppis_total, fill=gender)) +
  geom_boxplot() +
  theme(legend.position = "none") +
    scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
  labs(x = "Gender",
       y = "Teacher Privacy Invasion Scale Total",
       title = "Boxplot of Teacher Privacy Invasion Scale Total by Gender",
       tag = "Figure 4.") +
  theme_minimal()

@@

```{r}
#| label: boxplot-gender-ss-score
ggplot(communication, aes(gender, ss_score, fill=gender)) +
  geom_boxplot() + 
  scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
  theme(legend.position="none") +
  labs(x = "Gender",
       y = "Suspicion Scale Score",
       title = "Boxplot of Suspicion Scale Score by Gender",
       tag = "Figure 5.") +
  theme_minimal()

@@

There were no gender differences in student defensive behaviors. This indicates that students were not more defensive towards their teachers depending on student gender.
